---
title: "RMarkdownExample"
output: html_document
---

## Example R Markdown document

This example R Markdown file is associated with the tutorial that is currently located at <a href="https://github.com/jfobrycki/rmarkdown" target="_blank">https://github.com/jfobrycki/rmarkdown</a>

## Table of contents {#toc}

As described in the tutorial, these links provide an example of how to move to different sections within a report.

* [See the latest findings](#newfindings)
* [Research methods](#methods)

## This section shows the code chunk options

This is outside the codechunk. Everything here is run as Markdown/HTML.

```{r}
# This is a code chunk. As this code chunk was indicated as being written in R, everything in this code chunk runs as it would in R.
mean(cars$dist)
summary(cars$speed)
```

Include = TRUE

```{r, include = TRUE}
# True is the default in R Markdown
mean(cars$dist)
summary(cars$speed)
```

Include = FALSE

```{r, include = FALSE}
mean(cars$dist)
summary(cars$speed)
```

Echo = TRUE

```{r, echo = TRUE}
#True is the default in R Markdown
mean(cars$dist)
summary(cars$speed)
```


## New findings to report {#newfindings}

Here is a section where you can describe all the latest study findings. The link below will take you back to the table of contents section.

[Back to table of contents](#toc)

## Methods {#methods}

Similarly, you could describe the methods used in this section and then use the link below to move back to the table of contents.

[Back to table of contents](#toc)


## Tables

This section shows some of the example code about tables. 

 <table style="width:50%">
  <tr>
    <th>Column One</th>
    <th>Column Two</th>
  </tr>
  <tr>
    <td>Variable One</td>
    <td>Variable Two</td>
  </tr>
  <tr>
    <td>10</td>
    <td>40</td>
  </tr>
</table> 

Below is the example code with additional table options using the knitr::kable commands.

```{r}
# Create the aggregation by type and treatment
b<-aggregate(uptake~Type*Treatment,data=CO2,summary)
# See what this aggregate summary data looks like
b
# Split out the key uptake piece since all the summary columns are counted as only one column
e<-data.frame(round(b$uptake,2))
# Verify you are working with the summary statistics information
e
# Rename the columns
colnames(e)<-c("Min","1st Quart","Median","Mean","3rd Quart","Max")
# Group the information back together
cbind(b[,1:2],e) 
# Create a table and specify the alignment within each column
knitr::kable(cbind(b[,1:2],e),align="llcccccc",caption = "An example table caption.")
```


## Example of loading in the most recent file in a series

```{r}
# Show all the files in the directory
list.files()
# Created a sorted list of the files
# The pattern helps separate out files that might be in the same folder but not have the same naming structure
a<-sort(list.files(path="data/", pattern="ExampleDataset"),decreasing=TRUE)
# Create an object called filename using the first item listed
# This first item listed should be the most recent file, assuming that the files are numbered by date, for example.
filename<-a[1]
# Double check that this filename is the most recent file
filename
# Read in this file
#dataset<-read.csv(filename,header=T)
# Create an output in the R Markdown file that adds the filename to the report directly. This provides a double check for knowing which dataset is used for the entire report.
```

This report is created using the file `r print(filename)[1]`

This report is created on `r Sys.Date()`

## Example of running multiple languages in R Markdown

```{r}
#The below code will not run because the path names are generic
#saspath<- "C:/Program Files/NavigateToTheFinalFile/Version/sas.exe"
#statapath<- "C:/Program Files/NavigateToTheFinalFile/StataVersion/Stata.exe"
#sasopts <- "-nosplash -ls 75"
#knitr::opts_chunk$set(engine.path=list(sas=saspath,saslog=saspath,stata=statapath),engine.opts=list(sas=sasopts,saslog=sasopts),comment=NA)
```